Interisland movements of woodland caribou in Newfoundland

### 2020-02-19 paper/manuscript.Rmd
P1

Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration (Leblond et al.
2016) to avoid predators [@Bergerud_1985] and access islands during calving
(Bergerud et al. 1990). Swimming for quadrupedal terrestrial mammals can be
thought of as a set of trade-offs. Costs include high energy expenditure and
risk of drowning. Specifically, even though caribou are adept swimmers, the
energetic expenditure associated with swimming for quadrupedal mammals is
significantly higher than walking or running (Fish 1993). Additionally, drowning
is also possible (Miller & Gunn 1985) although the proportion of caribou that
die from drowning is unknown. Despite a large number of coastal and island
caribou herds, limited evidence exists suggesting that caribou swim in the ocean
as readily as they swim in freshwater (see Table 1). A key exception is Peary
caribou swimming up to 2.6 km between the Queen Elizabeth Islands (Miller 1995;
Miller 2002).

>>>>

Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration (Leblond et al.
2016) to avoid predators [@Bergerud_1985] and access islands during calving
(Bergerud et al. 1990). Swimming for quadrupedal terrestrial mammals can be
thought of as a set of trade-offs. Costs include high energy expenditure and
risk of drowning. Specifically, even though caribou are adept swimmers, the
energetic expenditure associated with swimming for quadrupedal mammals is
significantly higher than walking or running (Fish 1993), whiledrowning
is also possible (Miller & Gunn 1985). Despite a large number of coastal and
island caribou herds, only a handful of examples have documented caribou
swimming in the ocean (Table 1).
